Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/nlp.tex
Some edits including section numbering fixes.

The parsed output is then converted to the ICU Date Format Language described in Section 3.2 in order to effectively cross-validate results from the MDL algorithm. While this grammar accounts for the use of meridian markers `a.m.' and `p.m.' for the 12-hour format, ICU does not support these tokens, and they are simply ignored.

@@

\begin{itemize}
\item Restriction on the distribution of $30$ and $31$:
Months usually alternate between lengths of 30 and 31 days. We can use x mod 2 to get an alternating pattern of 1 and 0, then just add our constant base number of days:

@@

Now if we substitute this expression in the x + 1 dividend of Equation $2$, we can invert the pattern using our mask:

@@

\begin{itemize}
\item Similar to the MDL ranking properties described in Section 3.7, rules involving the non-terminal \texttt{DateGrammar} on the left-side of the rule, are assigned probability weights higher than those rules with the non-terminal being \texttt{TimeGrammar}. In practice, assigning $p(\texttt{DateGrammar} \rightarrow \beta_{1}) = 0.9$ and $p(\texttt{TimeGrammar} \rightarrow \beta_{2}) = 0.7$ leads to optimal ranking of the parse trees.

\item For the non-terminal symbol \texttt{Day}, the constraint specified is a range between 01 and 28-31, depending on month/year. However, for \texttt{dd} $> 12$, $p(\texttt{Day} \rightarrow d d) = 1.0$, and $0.5$ otherwise. This assignment helps disambiguate days from months.

>>>>

The parsed output is then converted to the ICU Date Format Language described in Section IIA in order to effectively cross-validate results from the MDL algorithm. While this grammar accounts for the use of meridian markers `a.m.' and `p.m.' for the 12-hour format, ICU does not support these tokens, and they are simply ignored.

@@

\begin{itemize}
\item Restriction on the distribution of $30$ and $31$:
Months usually alternate between lengths of $30$ and $31$ days. We can use $x \Mod 2$ to get an alternating pattern of 1 and 0, then just add our constant base number of days:

@@

Now if we substitute this expression in the $x + 1$ dividend of Equation $2$, we can invert the pattern using our mask:

@@

\begin{itemize}
\item Similar to the MDL ranking properties described in Section IIIG, rules involving the non-terminal \texttt{DateGrammar} on the left-side of the rule, are assigned probability weights higher than those rules with the non-terminal being \texttt{TimeGrammar}. In practice, assigning $p(\texttt{DateGrammar} \rightarrow \beta_{1}) = 0.9$ and $p(\texttt{TimeGrammar} \rightarrow \beta_{2}) = 0.7$ leads to optimal ranking of the parse trees.

\item For the non-terminal symbol \texttt{Day}, the constraint specified is a range between $01$ and $28-31$, depending on month/year. However, for \texttt{dd} $> 12$, $p(\texttt{Day} \rightarrow d d) = 1.0$, and $0.5$ otherwise. This assignment helps disambiguate days from months.
